### 2022-11-21 manuscript.Rmd
download intermediate_results if neccesary closes #16

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
  files:
    - intermediate_results.zip
---

@@

```{r}
intermediate_results <- here("intermediate_results/")
if(fs::dir_exists(intermediate_results))
 fs::dir_delete(intermediate_results)
unzip(here::here("intermediate_results.zip"))
```

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
---

@@

```{r}
intermediate_results <- here("intermediate_results.zip")
# manuscript is created from intermediate_files with two fallbacks:
# 1. if a intermediate_files.zip exists it is unpacked
# 2. if nothing exists, the zip is downloaded
if(!fs::dir_exists(fs::path_ext_remove(intermediate_results))){
  if(!fs::file_exists(intermediate_results))
    download.file("https://keeper.mpdl.mpg.de/f/d6526b78178c4b4199e9/?dl=1", intermediate_results)
  unzip(intermediate_results)
}
```
